\documentclass[11pt]{letter}


\setlength{\oddsidemargin}{-.10in}
\setlength{\textwidth}{6.7in}
\setlength{\textheight}{8.5in}
\setlength{\topmargin}{-.40in}

\begin{document}

\signature{Henry Wilde}

\begin{letter}{}

\opening{To whom it may concern,}

I am writing to you as a first year postgraduate research student within the 
School of Mathematics, Cardiff University. I have recently completed my B.Sc. 
Mathematics at Cardiff, graduating with First Class Honours, and have now begun 
a Ph.D. in Applied Statistics, Operational Research and Data Analytics. The 
purpose of this letter is to outline my motivation for applying for support from
EURO to attend NATCOR courses in the UK.

My research is focussed on the large-scale modelling of healthcare systems to 
better understand cost variations and increase the effectiveness of healthcare 
provision in the National Health Service, particularly in South Wales. The work
in this project will be reliant on a number of fields from pure and applied 
mathematics such as data analytics and stochastic modelling, but none more than
operational research. I believe it to be in my best interests to seize as many 
opportunities as possible to learn more about the field so as to help improve my
research. Even with the knowledge I have gained from my undergraduate modules, I
have been able to begin a promising line of research into how game-theoretic 
heuristics could be used to improve classification models. I do believe that 
attending courses with NATCOR will help me to obtain expert knowledge in, and 
draw inspiration from, higher-level concepts from operational research. In turn,
these experiences will help further lines of work around my main research as 
well as providing me with a stronger foundation from which to build my thesis.

It should also be noted that as a young academic, the fact that NATCOR 
represents a collaborative group of 13 universities means that my being able to 
attend their courses would help me begin some early networking in my field with
like-minded researchers and demonstrators from other universities.

In summary, I have hoped to convey that I am a keen and highly enthusiastic
mathematician with a burning desire to both learn and develop myself as a 
committed member of the operational research community. I thank you for your 
time in considering my application, and am at your disposal for any queries that
may arise.


\closing{Sincerely,}

\end{letter}


\end{document}
